Pleiotropy of expression quantitative trait loci increases with the number of regulated genes, active cell types and tissues and bound transcription factors

### 2022-12-13 ms/ms06_floats.tex
ENH

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% Fig 5: VEP consequences
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \begin{figure}[!tbp]
% \centering
% %
% \includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
% %
% \caption{Odds ratio of the variants annotated with given variant effect
% predictor (VEP) consequence and given GWAS class count compared with non
% pleiotropic variants with GWAS class count one. The significance is given for the
% q-value with False discovery rate 5\%.}
% \label{fig:vep_consequence}
% %
% \end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Fig 5: VEP consequences
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[!tbp]
\centering
%
\includegraphics[width=\textwidth]{\floatRelativePath/pltbar_vep_consequence.py/vep.png}
%
\caption{Odds ratio of the variants annotated with given variant effect
predictor (VEP) consequence and given GWAS class count compared with non
pleiotropic variants with GWAS class count one. The significance is given for the
q-value with False discovery rate 5\%.}
\label{fig:vep_consequence}
%
\end{figure}
